\chapter*{Acknowledgment}
\addcontentsline{toc}{chapter}{Acknowledgment}
\label{thanks}
First of all, I express my deepest gratitude to my advisor, Professor Rodney Van Meter.
The professor gave me a lot of advice and cared about me.
I feel very honored and blessed to have had the opportunity to study in Rod-san's seminars for 4 years.

I would like to thank the project lecturer Takahiko Satoh and the project assistant professor Michal Hajduˇsek, a faculty member in the same research group AQUA.
Thank you for mentoring me.

I would like to thank Naphan Benchasattabuse, my mentor in this thesis.
Whenever I asked a question, the answer always exceeded my expectations. 
He is a great mentor and I respect him very much.

I would also like to thank Takaaki Matsuo, Shin Nishio, Ryosuke Satoh and Yasuhiro Ohkura.
I am grateful for kind mentoring as a senior member of AQUA.
I definitely carry on the “Oi” as a AQUA tradition.

I would also like to thank my seminar colleagues, Makoto Nakai and Shigetora Miyashita.
It was a great pleasure to study quantum information and work on the same project together.

I would also like to thank Ai Toma, Shota Kusudo, Kengo Kumon, Yuta Morofuji, Yosuke Suda and Yu Yoshida.
They provided me with food, clothing and shelter for me. 
Without them, I could not have submitted my thesis.

Lastly, I would like to thank my family for bringing me up.
%%% Local Variables:
%%% mode: japanese-latex
%%% TeX-master: "../yummy_bthesis"
%%% End:
